---
title: "corr_workspace"
author: "Zack Grzywacz"
date: "October 30, 2020"
output: html_document
---


Not sure if i need all of these
```{r}
library(ncdf4)
library(raster)
library(lubridate)
library(ggplot2)
library(lattice)
library(rnaturalearth)
library(rnaturalearthdata)
library(rasterVis)
library(viridis)
library(seas)
library(s2dverification)
library(reshape2)
library(dplyr)
```



### Data Download from ECHAM5‐wiso (monthly, 1 degree grid)
https://zenodo.org/record/1249604#.XpnVbFNKhTZ

Data sources, years, extent (could be variables in function call someday)
SH extent can be changed to include pacific ocean, etc

!!!! Change this so it opens all of the files
Change the years?
Change the extent
```{r}
netcdf.file <- "data/d18O_precip_mon_1871_2011.nc"

F_yr <- 1958
L_yr <- 2011
years <- seq(F_yr, L_yr)
ext <- extent(0, 180, -90, 0) 
#ext <- extent(0, 180, -90, 0) #SH extent
```

Get a list of the variables to choose from and confirm that the time 
origin and units are appropriate......
(Units will be different for different files)
```{r}
nc <- ncdf4::nc_open(netcdf.file)

#select the variable
var.name <- names(nc[['var']])[1] #be sure this is the value you want

summary(nc$dim$lon$vals) #if longitude is 0-360 needs to be rotated
tunits <- ncdf4::ncatt_get(nc, "time", "units")
print(tunits)

ncdf4::nc_close(nc)
```

Rotate because the extent is 0-360 not 0-180 (takes a while)
(Make sure you need to do this for all files)
```{r}
dat <- rotate(brick(netcdf.file, varname= var.name))
```

Crop to spatial extent for faster processessing
(Crop to TAS for first part)
```{r}
datC <- crop(dat, ext)
```

!!! WRITE TO A FILE !!! so you don't have to open the netcdf files every time



### Composite Analysis on SAM
Extract Particular Years/Months from datC (climate raster brick)
!!Dont think I need to do this here

datY
```{r}
sel_y <- names(datC)[substr(names(datC), 2, 5) %in% years] 
#use that index to subset the raster brick
datY <- subset(datC, sel_y, value=T)
tail(names(datY), 30) 
```